Testing gene methylation enrichment analysis approaches using simulated data - summarise data

### 2023-11-26 figs/GSE158422_simulate_summary.Rmd
fig2
bugfix

x %>% kbl(caption="sim 100 res") %>% kable_paper("hover", full_width = F)

barplot(t(x),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.7, cex.axis=0.7, main="100 genes per set")
grid()

@@

>>>>

x3 %>% kbl(caption="sim 100 res") %>% kable_paper("hover", full_width = F)

barplot(t(x3),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.7, cex.axis=0.7, main="100 genes per set")
grid()

@@

# png
png(filename="fig2.png",height=150,width=210,units="mm",res=200)

par(mar = c(4.1, 4.1, 2.1, 0.5))
